Spec2Fab: A High-Fidelity Mapping from Specification to Fabrication

### 2012-08-01 paper.tex
need more citation

To generate BRDF
\begin{verbatim}
manager.setGenerator(stackingGenerator);
manager.setSimulator(brdfSimulator);
manager.setMetric(someImageMetric);
Shape shape("filename"), 
Image goal("filename1");
\end{verbatim}

Deformation
\begin{verbatim}
force = new Force(pos, dir, shapeID);
constraint = new Constraint(
    FIX_VERTEX, vertexList, shapeID));

@@

\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
A material with a particular
look and deformation properties is shown in Figure~\ref{fig:deform}

>>>>

To optimize BRDF for a particular camera view point and lighting.
\begin{verbatim}
scene.setCamera(camera);
scene.addLight(light);
manager.setGenerator(stackingGenerator);
manager.setSimulator(brdfSimulator);
manager.setMetric(someImageMetric);
Shape shape("filename"), 
Image goal("filename1");
\end{verbatim}

Defining elasticity properties
by specifying deformation 
reaction to a force applied to a point.

\begin{verbatim}
force = new Force(pos, dir, shapeID);
constraint = new Constraint(
    FIX_VERTEX, vertexList, shapeID));

@@

\section{Experiments}
\section{Print Material Characterization and Measurement}

\subsection{Previous Work}
Subsurface scattering. Mechanical properties
A material with a particular
look and deformation properties is shown in Figure~\ref{fig:deform}
